A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-22 results.tex
text changes

\noindent\textbf{Actionability:} Bug fix patterns related to attributes in Rust, such as adding or removing attributes can be valuable in designing program repair tools. For instance, by detecting and removing attributes that are no longer needed, program repair tools can optimize the codebase and eliminate unnecessary overhead. On the other hand, when adding an attribute, these patterns offer insights into how repair tools can manipulate attributes and modify other parts of the code accordingly to make it adhere to the user's specifications.

>>>>

\noindent\textbf{Actionability:} Bug fix patterns related to attributes in Rust, such as removing or adding attributes can be valuable in designing program repair tools. For instance, by recognizing situations where attributes are no longer needed, program repair tools can propose changes that optimize the codebase and eliminate unnecessary overhead. On the other hand, a repair tool could also recognize situations where attributes need to be added, enabling the code to better adhere to the user's specifications.
